Machine Learned Models for Estimation of Sleep Quality in Free-Living Accelerometer Data

### 2023-01-26 presentation/index.qmd
make html file self-contained

---
title: "Machine Learned Models for Estimation of Sleep Quality in Free-Living Accelerometer Data"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs: 
    smaller: true
    theme: moon
    slide-number: true
    chalkboard: 
      buttons: false
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---

>>>>

---
title: "Machine Learned Models for Estimation of Sleep Quality in Free-Living Accelerometer Data"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: true
    theme: moon
    slide-number: true
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---
